% Academic CV - Clean single-column template
\documentclass[11pt, letterpaper]{article}

% Page geometry
\usepackage[margin=1in]{geometry}

% Fonts - modern sans-serif
\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

% Packages
\usepackage[hidelinks]{hyperref}
\usepackage{etaremune}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{datetime2}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
    pdftitle={Jeremiah Cha -- Academic Curriculum Vitae},
    pdfauthor={Jeremiah Cha},
    pdfsubject={Academic CV},
    pdfkeywords={Jeremiah Cha, curriculum vitae, CV, political science, Harvard}
}

% Section formatting
\titleformat{\section}
    {\large\bfseries\scshape\color{black}}
    {}
    {0em}
    {}
    [\titlerule]
\titlespacing*{\section}{0pt}{2ex plus 1ex minus .2ex}{1.5ex plus .2ex}

% Remove page numbers
\pagenumbering{gobble}

% Custom commands
\newcommand{\entry}[2]{\noindent #1 \hfill #2\\}
\newcommand{\subentry}[1]{\hspace*{1em}#1\\}
\newcommand{\subentrydate}[2]{\hspace*{1em}#1 \hfill #2\\}

% Reduce list spacing
\setlist[enumerate]{itemsep=0.5ex, parsep=0pt, topsep=0.5ex}

\begin{document}

% Header
\begin{center}
    {\Huge\bfseries Jeremiah Cha}\\[1ex]
    CGIS Knafel, 1737 Cambridge St, Cambridge, MA 02138\\[0.5ex]
    \href{mailto:jeremiahcha@g.harvard.edu}{jeremiahcha@g.harvard.edu} ~$\cdot$~
    \href{https://www.jeremiahcha.com}{www.jeremiahcha.com} ~$\cdot$~
    \href{https://orcid.org/0000-0003-3199-3386}{orcid.org/0000-0003-3199-3386}
\end{center}

\vspace{1ex}

\section{Academic Appointments}
\entry{\textbf{American University}}{2027-}
\subentry{Assistant Professor of Government}

\entry{\textbf{Princeton University}}{2026-2027}
\subentry{Post-doctoral Fellow, Center for the Study of Democratic Politics}

\section{Education}

\entry{\textbf{Harvard University}}{Expected 2026}
\subentry{Ph.D., Government}
\subentry{\small Dissertation: ``Racial Representation in American Local Politics''}
\subentry{\small Committee: James M. Snyder, Jr., Stephen D. Ansolabehere, Taeku Lee, Stephanie Ternullo}
\subentrydate{A.M., Government}{2022}

\vspace{0.5ex}
\entry{\textbf{University of California, San Diego}}{2019}
\subentry{B.A., Political Science (High Honors), \textit{magna cum laude}}

\section{Peer-Reviewed Publications}

\begin{etaremune}
    \item Cha, Jeremiah, and Jon C. Rogowski. (2025). \href{https://onlinelibrary.wiley.com/doi/10.1111/lsq.70028}{``Mechanisms of checks and balances: Appropriations, congressional committees, and interbranch conflict.''} \emph{Legislative Studies Quarterly} 50(3).
    \item Cha, Jeremiah, Justin Gest, and Tom K. Wong. (2025). \href{https://www.cambridge.org/core/journals/journal-of-race-ethnicity-and-politics/article/abs/dilemmas-in-representation-immigration-identity-and-political-parties/212CAAFE1CD364A32E8C09B23832A0A0}{``Dilemmas in representation: Immigration, identity, and political parties.''} \emph{Journal of Race, Ethnicity, and Politics} 10(3).
\end{etaremune}

\section{Working Papers}

\begin{etaremune}
    \item ``Building Representation: The Politics of Development, Diversity, and Institutional Norms''
    \item ``Measuring Issue Racialization''
    \item ``Preaching to the (After School) Choir: Studying Representation and Racialized Agendas Using School Board Meetings'' (with Hunter Rendleman and Tyler Simko)
\end{etaremune}

\section{Selected Works in Progress}

\begin{etaremune}
    \item ``Identifying Local Civil Service'' (with Justin de Benedictis-Kessner)
    \item ``Revisiting Committees: Evaluating Theories of Legislative Organization'' (with Sooahn Shin)
\end{etaremune}

\section{Data}

\begin{etaremune}
    \item Cha, Jeremiah, Shiro Kuriwaki, and James M. Snyder, Jr. (2025). ``Candidates in American General Elections.'' Harvard Dataverse. \textsc{doi}: \href{https://doi.org/10.7910/DVN/DGDRDT}{\texttt{10.7910/DVN/DGDRDT}}.
\end{etaremune}

\section{Non-Refereed Publications}

\begin{etaremune}
    \item Cha, Jeremiah. (2025). ``Electing foreign-born legislators show more support for permissive immigration policies in the US, but not in the UK or Canada.'' \emph{LSE Phelan US Centre}.
    \item Devlin, Kat, Regina Widjaya, and Jeremiah Cha. (2020). ``For global legislators on Twitter, an engaged minority creates outsize share of content.'' \emph{Pew Research Center}.
    \item Cha, Jeremiah. (2020). ``Fast facts about South Koreans' views of democracy as legislative election nears.'' \emph{Pew Research Center}.
    \item Cha, Jeremiah. (2020). ``People in Asia-Pacific regard the U.S. more favorably than China, but Trump gets negative marks.'' \emph{Pew Research Center}.
    \item Huang, Christine, and Jeremiah Cha. (2020). ``Russia and Putin receive low ratings globally.'' \emph{Pew Research Center}.
    \item Fetterolf, Janell, and Jeremiah Cha. (2020). ``Few in other countries approve of Trump's major foreign policies, but Israelis are an exception.'' \emph{Pew Research Center}.
    \item Wong, Tom K., Jeremiah Cha, and Erika Villareal-Garcia. (2019). ``The impact of changes to the public charge rule on undocumented immigrants living in the United States.'' \emph{U.S. Immigration Policy Center (USIPC) at UC San Diego}.
    \item Silver, Laura, Emily A. Vogels, Mara Mordecai, Jeremiah Cha, Raea Rasmussen, and Lee Rainie. (2019). ``Mobile divides in emerging economies.'' \emph{Pew Research Center}.
    \item Cha, Jeremiah. (2017). ``Dreaming of DACA.'' \emph{Claremont Journal of Law and Public Policy}.
\end{etaremune}

\section{Fellowships, Grants, and Awards}

\entry{Honorable Mention, Bryan Jackson Dissertation Award}{2025}
\subentry{\textit{APSA Urban and Local Politics Section}}
\entry{Pre-Doctoral Fellow, Election Law Clinic}{2025}
\subentry{\textit{Harvard Law School}}
\entry{Teaching Recognition}{2023, 2024}
\subentry{\textit{Harvard Undergraduate Association}}
\entry{CAPS Seed Grant (with Angelo Dagonel and Kiara Hernandez)}{2022}
\subentry{\textit{Harvard University Center for American Political Studies}}
\entry{Harvard GSC Conference Grant}{2022}
\subentry{\textit{Harvard University GSAS}}
\entry{V.O. Key Fellowship}{2020--2024}
\subentry{\textit{Harvard University GSAS}}
\entry{Phi Beta Kappa}{2019}
\entry{Pi Sigma Alpha}{2017}

\section{Selected Presentations}

\entry{APSA}{2023, 2024, 2025}
\subentrydate{Local Political Economy Conference}{2025}
\entry{MPSA}{2023, 2024, 2025}
\entry{Tufts University}{2023}
\entry{Pew Research Center}{2020}

\section{Teaching and Advising}

\textbf{Harvard College, Department of Government}\\
GOV 30, American Government: A New Perspective (Head TF) \hfill Fall 2023, 2024\\
GOV 51, Data Analysis and Politics (TF) \hfill Spring 2023, 2024\\
GOV 30, American Government: A New Perspective (TF) \hfill Fall 2022

\vspace{1ex}
\noindent\textbf{Undergraduate Thesis Advising}\\
Jack Holland (Government) \hfill Harvard '26\\
Aaron Shuchman (Government) \hfill Harvard '25\\
Ava Pallotta (Government) \hfill Harvard '25\\
Oliver Adler (Government) \hfill Harvard '24

\section{Service}

\textbf{Referee}\\
\textit{American Political Science Review (APSR) (1), American Journal of Political Science (AJPS) (1), British Journal of Political Science (BJPS) (1)}

\vspace{1ex}
\noindent\textbf{Harvard University}\\
American Politics Speaker Series Coordinator \hfill 2022--2023, 2024--2025\\
Diversity Committee \hfill 2020--2024\\
American Politics Research Workshop Coordinator \hfill 2022--2023\\
Communications Officer, Harvard Government GSA \hfill 2022--2023\\
Rules and Election Officer, Harvard Government GSA \hfill 2021--2023

\section{Non-Academic Experience}

\entry{Pew Research Center, Global Attitudes Project, Research Assistant}{2019-2020}
\entry{Brookings Institution Governance Studies, Intern}{2018}
\entry{House of Representatives, Intern}{2017}
\entry{House of Representatives, Intern}{2016}
\entry{Chaminade College Preparatory High School, Debate Coach}{2015--2018}

\section{Skills}

\noindent\textbf{Technical:} R, Python, Stata, SPSS, \LaTeX, HTML\\
\textbf{Language:} English (Native), Korean (Limited Working)

\vfill
\hfill \small{\textit{Updated \today}}

\end{document}
